---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# corpdiss: A corpus-based model of dissonance perception

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/pmcharrison/corpdiss.svg?branch=master)](https://travis-ci.org/pmcharrison/corpdiss)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/corpdiss?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/corpdiss)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/corpdiss/badge.svg)](https://coveralls.io/r/pmcharrison/corpdiss?branch=master)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2545748.svg)](https://doi.org/10.5281/zenodo.2545748)

The `corpdiss` R package implements a corpus-based model of dissonance perception.
This model represents the idea that dissonance decreases through familiarity, 
and therefore perceptual dissonance should decrease in proportion to 
a chord's prevalence in a given musical style.

## Installation

You can install the current version of `corpdiss` from Github by entering
the following commands into R:

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("corpdiss")
```

## Example usage

### Estimating chordal consonance

The `corpus_dissonance` function estimates the consonance of an individual chord.

```{r}
library(corpdiss)

# Major triad, root position
corpus_dissonance(c(60, 64, 67))

# Major triad, first inversion
corpus_dissonance(c(64, 67, 72))

# Minor triad, root position
corpus_dissonance(c(60, 63, 67))

# Diminished triad
corpus_dissonance(c(60, 63, 66))

# Augmented triad
corpus_dissonance(c(60, 64, 67))
```

By default, the `corpus_dissonance` function uses chord prevalences 
extracted from the McGill Billboard dataset (Burgoyne, 2011).
The dataset's contents were sampled from the Billboard magazine's
United States "Hot 100" chart between 1958 and 1991,
and transcribed by expert musicians.

By default,
the dissonance estimation treats chords as transposition invariant,
and chord pitches as octave-invariant,
but differentiates between different inversions of the same chord.
Different behaviour can be achieved by passing a custom corpus analysis
to `corpus_dissonance` (see `?corpus_dissonance` for more details).

### Adding new corpora

It is easy to analyse dissonance using a different corpus,
or a different chord representation.

```{r}
corpus <- hcorp::classical_1[1:5]
analysis <- corpus_dissonance_table(corpus, type = "pc_set", add = 0)
chord <- c(60, 64, 67)
corpus_dissonance(chord, analysis)
```
